TODO

### 2021-03-16 publications/The_tool_intro/paper.tex
tool_intro:short P4 description

	\section{Introduction}
	% P4 (max 1-1.5 hasáb) - példa (később használandó a többihez) - Máté
	P4 \cite{p4paper} is a high level, domain-specific programming language. It is developed mainly for
describing the data plane layer of packet processing algorithms of different network
devices (e.g. switches, routers) in a protocol and target independent way.

>>>>

	\section{Introduction}
	% P4 (max 1-1.5 hasáb) - példa (később használandó a többihez) - Máté
	P4~\cite{p4paper} is a high level, domain-specific programming language. It is developed mainly for
describing the data plane layer of packet processing algorithms of different network
devices (e.g. switches, routers) in a protocol and target independent way. Figure~\ref{code:P4} illustrates a P4 program. The program first defines the applied header structure, than the parser part describes how the fields of the defined headers will be set from the input bit stream (input packet). Controller part can modify values of headers' fields and metadatas by applying lookup tables. The dataplane program describes the structure of the tables, the key fields based on that lookups will be executed and the possible results of the lookups, namely the applicable actions. However concrete data of the tables (which actions will be executed with wich parameters for which key values) are defined by the controlplane program, therefore it will not appear in P4. Finally the deparse part defines how the output bitstream (output packet) will be created from the headers.
